### 2024-03-25 thesis/sections/6.2-re-generation.tex
results

        {1}                           & {2}    & {70,49}                             & {54,73}                             & {7,29}                                   & {70,16}          & {85,06}          & {13,06}         & {11,68}       & {32,25}     & {34,03}     \\
        {1}                           & {10}   & {78,26}                             & {63,33}                             & {3,56}                                   & {68,97}          & {85,01}          & {10,85}         & {12,72}       & {32,77}     & {33,85}     \\
        {1}                           & {16}   & {74,18}                             & {52,21}                             & {5,38}                                   & {71,57}          & {86,87}          & {10,72}         & {13,19}       & {33,64}     & {33,33}     \\
        {1}                           & {50}   & {70,83}                             & {43,56}                             & {4,21}                                   & {65,23}          & {83,11}          & {12,54}         & {11,81}       & {33,14}     & {34,72}     \\
        {1}                           & {100}  & {73,18}                             & {52,14}                             & {3,86}                                   & {60,94}          & {80,85}          & {20,36}         & {13,67}       & {33,71}     & {33,64}     \\
        {2}                           & {2}    & {72,31}                             & {50,42}                             & {5,52}                                   & {66,2}           & {83,39}          & {14,42}         & {13,32}       & {33,62}     & {32,73}     \\
        {2}                           & {10}   & {75,22}                             & {58,4}                              & {3,99}                                   & {73,22}          & {87,68}          & {9,03}          & {12,37}       & {33,3}      & {34,11}     \\
        {2}                           & {16}   & {\textbf{81,64}}                    & {\textbf{73,66}}                    & {\textbf{2,86}}                          & {73,44}          & {88,21}          & {8,85}          & {12,98}       & {33,94}     & {34,24}     \\
        {2}                           & {50}   & {74,39}                             & {48,53}                             & {3,17}                                   & {\textbf{75,35}} & {\textbf{88,77}} & {\textbf{8,07}} & {14,19}       & {33,04}     & {33,46}     \\
        {2}                           & {100}  & {74,09}                             & {54,88}                             & {3,65}                                   & {54,56}          & {76,95}          & {22,57}         & {13,28}       & {32,8}      & {33,38}     \\
        {3}                           & {2}    & {71,03}                             & {50,76}                             & {4,62}                                   & {65,18}          & {82,68}          & {14,23}         & {12,76}       & {33,58}     & {33,64}     \\
        {3}                           & {10}   & {76,91}                             & {59,42}                             & {2,6}                                    & {71,66}          & {87,14}          & {9,9}           & {12,54}       & {32,75}     & {33,85}     \\
        {3}                           & {16}   & {79,95}                             & {67,55}                             & {3,17}                                   & {50,13}          & {73,24}          & {24,22}         & {12,93}       & {33,79}     & {34,46}     \\
        {3}                           & {50}   & {62,93}                             & {48,03}                             & {16,58}                                  & {\textbf{76,09}} & {\textbf{88,5}}  & {\textbf{9,2}}  & {13,67}       & {33,73}     & {34,29}     \\
        {3}                           & {100}  & {75,74}                             & {57,51}                             & {2,43}                                   & {69,7}           & {86,14}          & {9,38}          & {13,02}       & {33,64}     & {34,2}      \\
        {4}                           & {2}    & {41,23}                             & {42,53}                             & {35,33}                                  & {63,93}          & {82,34}          & {15,3}          & {12,2}        & {33,25}     & {33,64}     \\
        {4}                           & {10}   & {78,99}                             & {66,4}                              & {2,08}                                   & {73,22}          & {88,01}          & {10,85}         & {12,5}        & {33,55}     & {33,16}     \\
        {4}                           & {16}   & {\textbf{80,08}}                    & {\textbf{70,48}}                    & {\textbf{3,47}}                          & {69,4}           & {86,09}          & {10,63}         & {11,72}       & {33,1}      & {34,03}     \\
        {4}                           & {50}   & {75,48}                             & {54,44}                             & {3,34}                                   & {71,35}          & {86,61}          & {10,68}         & {11,81}       & {33,18}     & {34,33}     \\
        {4}                           & {100}  & {74,78}                             & {57,09}                             & {3,86}                                   & {59,2}           & {80,14}          & {20,57}         & {12,67}       & {32,3}      & {34,55}     \\
        {6}                           & {2}    & {72,87}                             & {51,44}                             & {2,78}                                   & {60,82}          & {80,42}          & {17,07}         & {13,45}       & {33,73}     & {33,64}     \\
        {6}                           & {10}   & {73,61}                             & {48,73}                             & {2,82}                                   & {32,64}          & {58,42}          & {33,12}         & {11,89}       & {33,15}     & {35,03}     \\
        {6}                           & {16}   & {73,52}                             & {49,67}                             & {2,43}                                   & {49,39}          & {73,19}          & {23,78}         & {13,06}       & {32,31}     & {34,64}     \\
        {6}                           & {50}   & {44,31}                             & {45,07}                             & {33,29}                                  & {\textbf{78,82}} & {\textbf{90,22}} & {\textbf{7,29}} & {12,72}       & {33,29}     & {32,99}     \\
        {6}                           & {100}  & {\textbf{80,95}}                    & {\textbf{69,88}}                    & {\textbf{3,34}}                          & {62,2}           & {80,62}          & {19,88}         & {14,24}       & {32,36}     & {32,94}     \\

@@

                                      &         & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}} & \multicolumn{3}{c}{\textbf{CLEVR colour}}                                                                                                                                                                                                           \\  \cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
        $n$                           & $|V|$   & \textbf{A\textsubscript{color}}     & \textbf{A\textsubscript{shape}}     & \textbf{A\textsubscript{size}}            & \textbf{A\textsubscript{color}} & \textbf{A\textsubscript{shape}} & \textbf{A\textsubscript{size}} & \textbf{A\textsubscript{color}} & \textbf{A\textsubscript{shape}} & \textbf{A\textsubscript{size}} \\\midrule
        \multicolumn{2}{c|}{baseline} & {92,03} & {88,91}                             & {50,55}                             & {89,38}                                   & {80,78}                         & {49,92}                         & {90,78}                        & {100}                           & {76,72}                                                          \\\midrule
        {1}                           & {2}     & {93,68}                             & {89,69}                             & {52,04}                                   & {90,12}                         & {88,09}                         & {49,74}                        & {87,37}                         & {100}                           & {76,56}                        \\
        {1}                           & {10}    & {94,21}                             & {96,31}                             & {52,78}                                   & {90,15}                         & {90,6}                          & {49,74}                        & \textbf{91,32}                  & {100}                           & {76,52}                        \\
        {1}                           & {16}    & {92,8}                              & {94,97}                             & {52,78}                                   & {93,45}                         & {91,97}                         & {49,74}                        & {91,03}                         & {100}                           & {76,52}                        \\
        {1}                           & {50}    & {91,58}                             & {90,1}                              & {52,78}                                   & {93,39}                         & {94,66}                         & {49,74}                        & {89,41}                         & {100}                           & {76,52}                        \\
        {1}                           & {100}   & {92,66}                             & {90,41}                             & {52,78}                                   & {90,23}                         & {83,03}                         & {49,74}                        & {86,72}                         & {100}                           & {76,52}                        \\
        {2}                           & {2}     & {92,45}                             & {92,45}                             & {52,04}                                   & \textbf{94,38}                  & {88,72}                         & {49,74}                        & {88,89}                         & {100}                           & {76,56}                        \\
        {2}                           & {10}    & {\textbf{94,44}}                    & {96,09}                             & {52,78}                                   & {90,71}                         & {91,54}                         & {49,74}                        & {89,54}                         & {100}                           & {76,52}                        \\
        {2}                           & {16}    & {92,66}                             & {90,58}                             & {52,78}                                   & {94,14}                         & \textbf{97,18}                  & {49,74}                        & {86,98}                         & {100}                           & {76,52}                        \\
        {2}                           & {50}    & {92,45}                             & {89,28}                             & {52,78}                                   & {93,01}                         & {92,01}                         & {49,74}                        & {86,5}                          & {100}                           & {76,52}                        \\
        {2}                           & {100}   & {92,97}                             & {\textbf{98,91}}                    & {52,78}                                   & {92,49}                         & {92,66}                         & {49,74}                        & {86,68}                         & {100}                           & {76,52}                        \\
        {3}                           & {2}     & {93,32}                             & {90,97}                             & {52,04}                                   & {92,53}                         & {87,88}                         & {49,74}                        & {90,58}                         & {100}                           & {76,56}                        \\
        {3}                           & {10}    & \textbf{{94,79}}                    & {97,01}                             & {52,78}                                   & {92,8}                          & {94,4}                          & {49,74}                        & \textbf{91,17}                  & {100}                           & {76,52}                        \\
        {3}                           & {16}    & {93,1}                              & {95,36}                             & {52,78}                                   & {91,88}                         & {86,72}                         & {49,74}                        & {88,06}                         & {100}                           & {76,52}                        \\
        {3}                           & {50}    & {90,84}                             & {90,93}                             & {52,78}                                   & \textbf{94,18}                  & {94,92}                         & {49,74}                        & {88,59}                         & {100}                           & {76,52}                        \\
        {3}                           & {100}   & {90,76}                             & {89,37}                             & {52,78}                                   & {92,8}                          & {94,1}                          & {49,74}                        & \textbf{91,84}                  & {100}                           & {76,52}                        \\
        {4}                           & {2}     & {92,11}                             & {94,86}                             & {52,04}                                   & {93,86}                         & {88,56}                         & {49,74}                        & {87,11}                         & {100}                           & {76,56}                        \\
        {4}                           & {10}    & {92,75}                             & {90,58}                             & {52,78}                                   & {93,71}                         & {95,05}                         & {49,74}                        & {89,89}                         & {100}                           & {76,52}                        \\
        {4}                           & {16}    & {94,14}                             & {\textbf{98,57}}                    & {52,78}                                   & {\textbf{95,23}}                & \textbf{96,14}                  & {49,74}                        & {88,06}                         & {100}                           & {76,52}                        \\
        {4}                           & {50}    & {93,32}                             & {95,66}                             & {52,78}                                   & {90,45}                         & {91,01}                         & {49,74}                        & {88,85}                         & {100}                           & {76,52}                        \\
        {4}                           & {100}   & {93,58}                             & {89,41}                             & {52,78}                                   & {93,19}                         & {94,66}                         & {49,74}                        & {86,98}                         & {100}                           & {76,52}                        \\
        {6}                           & {2}     & {92,94}                             & {93,39}                             & {52,04}                                   & {92,16}                         & {82,18}                         & {49,74}                        & {90,05}                         & {100}                           & {76,56}                        \\
        {6}                           & {10}    & {\textbf{94,23}}                    & {\textbf{98,78}}                    & {52,78}                                   & {92,75}                         & \textbf{96,79}                  & {49,74}                        & {87,67}                         & {100}                           & {76,52}                        \\
        {6}                           & {16}    & {91,32}                             & {96,96}                             & {52,78}                                   & {93,75}                         & {95,57}                         & {49,74}                        & {89,37}                         & {100}                           & {76,52}                        \\
        {6}                           & {50}    & {91,45}                             & {88,28}                             & {52,78}                                   & {86,24}                         & {91,71}                         & {49,74}                        & {88,32}                         & {100}                           & {76,52}                        \\
        {6}                           & {100}   & {92,45}                             & {94,92}                             & {52,78}                                   & {93,62}                         & {95,3}                          & {49,74}                        & {89,19}                         & {100}                           & {76,52}                        \\

@@

Finally, Table \ref{tab:results:attribute-predictor-game} show the results for the games in which the receiver predicts a one-hot vector of the attributes.
Again, the baselines are games, the receiver plays alone.
Hereby, it can be seen that the receiver can already predict the \emph{color} and \emph{shape} very well: 92\% and 88,91\% respectively on the \emph{Dale-2} dataset, 89,38\% and 80,78\% respectively on the \emph{Dale-5} dataset, and 90,78\% and 100\% respectively on the \emph{CLEVR color} dataset.
The \emph{size} however corresponds to a random guess on the \emph{Dale} dataset and only achieves 76,72\% on the \emph{CLEVR color} dataset.

\begin{table}[ht]
    \centering
    \begin{tabular}{ccc|ccc|ccc}
        \toprule
              &         &         & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}}                                                                             \\\cmidrule(lr){4-6}\cmidrule(lr){7-9}
        $|V|$ & $h_{s}$ & $h_{r}$ & \textbf{Acc.}                       & \textbf{word-by-word}               & \textbf{length} & \textbf{Acc.} & \textbf{word-by-word} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}    & {22,9\%}                            & {62,8\%}                            & {1}             & {7,1\%}       & {40\%}                & {1}             \\
        {13}  & {10}    & {10}    & {22,8\%}                            & {62,9\%}                            & {0}             & {7,3\%}       & {38,7\%}              & {1}             \\
        {20}  & {10}    & {10}    & {24,6\%}                            & {64\%}                              & {1}             & {6,7\%}       & {38,7\%}              & {1}             \\
        {100} & {10}    & {10}    & {24,4\%}                            & {62\%}                              & {1}             & {7,8\%}       & {40\%}                & {1}             \\
        {100} & {100}   & {100}   & {21\%}                              & {62\%}                              & {1}             & {6,5\%}       & {37,8\%}              & {1}             \\
        \bottomrule
    \end{tabular}
    \caption{Results of the caption generator: $|V|$ are different vocabulary sizes and $h$ hidden sizes.}
    % SD: What is word-by-word?
    % DK: the same as in the caption generator with a single model (QUESTION)
    \label{tab:results_caption_generator_game}
\end{table}

The results of the caption generator game are summarized in Table \ref{tab:results_caption_generator_game}.
In general, it can be seen that the agents have much bigger problems, to solve the task together than a single neural network.
The highest accuracy for descriptions, the agents manage to predict correctly is at 24,6\% for images of the 'Dale-2' dataset.
Compared to the (masked) accuracy of the single model with 72\%, the agents predict 47,4\% points less correct descriptions.
A similar worse performance can be seen for the 'Dale-5' dataset.
Here, the agents only manage to produce for 7,8\% of the images correct descriptions with a vocabulary size of 100, 13,2\% points less than the single neural model.
The same effect can be seen for the word-by-word accuracy, which is much lower than the metric for the single neural model for both datasets.
% SD: With the vocabulary size of 100.
% DK: (done)

When looking, how the different variables affect the performance, it can be seen that a bigger vocabulary size tends to help the agents.
% SD: Not sure. The difference is still very small, within a couple of %.
% DK: TODO
This is only visible for the 'Dale-2' dataset.
With constant hidden sizes of 10, the agents score around 22,9\% with only 10 and 13 available symbols.
When this is increased to 20 and respectively 100 symbols, the agents can increase their accuracy to around 24,5\%.
However, the increase is relatively small.
Interestingly, this effect only occurs, when the hidden sizes are small with only 10 dimensions.
As soon as they are increased to 100 dimensions with a vocabulary size of 100 symbols, the accuracy drops to 21\%.
% SD: Very small decerase for such a large difference in vocabulary size compared to what we have seen earlier.
% DK: TODO

Looking at the 'Dale-5' dataset, the increase is still there, when the vocabulary is increased to 100 symbols.
Nonetheless, the difference is with 0,5\% points even smaller and the reason may be due to other influences, such as the random initialization of the weights of the agents.
This is confirmed, when looking at emerged languages.
In all the setups, the same message is communicated for all samples, independently of the input image.
This is also reflected in the length of the messages.
For the setup with a vocabulary size of $|V| = 13$, no message is transferred, and the accuracy stays the same as in the other setups.
% SD: Here it would be much better to have a loss curve to show differences in loss between the number of communication events, the same could also be done for accuracy. Then we would have a clearer picture of how vocabulary size affects learning. It could be that with 100 vocabulary there is actually a better performance than before the final cut-off point. Is this possible? How was the final cut-off point determined anyway?
% DK: TODO

>>>>

        {1}                           & {2}    & {70,49}                             & {54,73}                             & {7,29}                                   & {70,16}                   & {85,06}                   & {13,06}                   & \textcolor{purple}{11,68} & \textcolor{purple}{32,25} & \textcolor{purple}{34,03} \\
        {1}                           & {10}   & {78,26}                             & {63,33}                             & {3,56}                                   & {68,97}                   & {85,01}                   & {10,85}                   & \textcolor{purple}{12,72} & \textcolor{purple}{32,77} & \textcolor{purple}{33,85} \\
        {1}                           & {16}   & {74,18}                             & {52,21}                             & {5,38}                                   & {71,57}                   & {86,87}                   & {10,72}                   & \textcolor{purple}{13,19} & \textcolor{purple}{33,64} & \textcolor{purple}{33,33} \\
        {1}                           & {50}   & {70,83}                             & \textcolor{purple}{43,56}           & {4,21}                                   & {65,23}                   & {83,11}                   & {12,54}                   & \textcolor{purple}{11,81} & \textcolor{purple}{33,14} & \textcolor{purple}{34,72} \\
        {1}                           & {100}  & {73,18}                             & {52,14}                             & {3,86}                                   & \textcolor{purple}{60,94} & \textcolor{purple}{80,85} & \textcolor{purple}{20,36} & \textcolor{purple}{13,67} & \textcolor{purple}{33,71} & \textcolor{purple}{33,64} \\
        {2}                           & {2}    & {72,31}                             & {50,42}                             & {5,52}                                   & {66,2}                    & {83,39}                   & {14,42}                   & \textcolor{purple}{13,32} & \textcolor{purple}{33,62} & \textcolor{purple}{32,73} \\
        {2}                           & {10}   & {75,22}                             & {58,4}                              & {3,99}                                   & {73,22}                   & {87,68}                   & {9,03}                    & \textcolor{purple}{12,37} & \textcolor{purple}{33,3}  & \textcolor{purple}{34,11} \\
        {2}                           & {16}   & {\textbf{81,64}}                    & {\textbf{73,66}}                    & {\textbf{2,86}}                          & {73,44}                   & {88,21}                   & {8,85}                    & \textcolor{purple}{12,98} & \textcolor{purple}{33,94} & \textcolor{purple}{34,24} \\
        {2}                           & {50}   & {74,39}                             & {48,53}                             & {3,17}                                   & {\textbf{75,35}}          & \textbf{88,77}            & \textbf{8,07}             & \textcolor{purple}{14,19} & \textcolor{purple}{33,04} & \textcolor{purple}{33,46} \\
        {2}                           & {100}  & {74,09}                             & {54,88}                             & {3,65}                                   & \textcolor{purple}{54,56} & \textcolor{purple}{76,95} & \textcolor{purple}{22,57} & \textcolor{purple}{13,28} & \textcolor{purple}{32,8}  & \textcolor{purple}{33,38} \\
        {3}                           & {2}    & {71,03}                             & {50,76}                             & {4,62}                                   & {65,18}                   & \textcolor{purple}{82,68} & {14,23}                   & \textcolor{purple}{12,76} & \textcolor{purple}{33,58} & \textcolor{purple}{33,64} \\
        {3}                           & {10}   & {76,91}                             & {59,42}                             & {2,6}                                    & {71,66}                   & {87,14}                   & {9,9}                     & \textcolor{purple}{12,54} & \textcolor{purple}{32,75} & \textcolor{purple}{33,85} \\
        {3}                           & {16}   & {79,95}                             & {67,55}                             & {3,17}                                   & \textcolor{purple}{50,13} & \textcolor{purple}{73,24} & {24,22}                   & \textcolor{purple}{12,93} & \textcolor{purple}{33,79} & \textcolor{purple}{34,46} \\
        {3}                           & {50}   & {62,93}                             & {48,03}                             & {16,58}                                  & {\textbf{76,09}}          & {\textbf{88,5}}           & \textbf{9,2}              & \textcolor{purple}{13,67} & \textcolor{purple}{33,73} & \textcolor{purple}{34,29} \\
        {3}                           & {100}  & {75,74}                             & {57,51}                             & {2,43}                                   & {69,7}                    & {86,14}                   & {9,38}                    & \textcolor{purple}{13,02} & \textcolor{purple}{33,64} & \textcolor{purple}{34,2}  \\
        {4}                           & {2}    & \textcolor{purple}{41,23}           & \textcolor{purple}{42,53}           & \textcolor{purple}{35,33}                & {63,93}                   & \textcolor{purple}{82,34} & {15,3}                    & \textcolor{purple}{12,2}  & \textcolor{purple}{33,25} & \textcolor{purple}{33,64} \\
        {4}                           & {10}   & {78,99}                             & {66,4}                              & {2,08}                                   & {73,22}                   & {88,01}                   & {10,85}                   & \textcolor{purple}{12,5}  & \textcolor{purple}{33,55} & \textcolor{purple}{33,16} \\
        {4}                           & {16}   & {\textbf{80,08}}                    & {\textbf{70,48}}                    & {\textbf{3,47}}                          & {69,4}                    & {86,09}                   & {10,63}                   & \textcolor{purple}{11,72} & \textcolor{purple}{33,1}  & \textcolor{purple}{34,03} \\
        {4}                           & {50}   & {75,48}                             & {54,44}                             & {3,34}                                   & {71,35}                   & {86,61}                   & {10,68}                   & \textcolor{purple}{11,81} & \textcolor{purple}{33,18} & \textcolor{purple}{34,33} \\
        {4}                           & {100}  & {74,78}                             & {57,09}                             & {3,86}                                   & \textcolor{purple}{59,2}  & \textcolor{purple}{80,14} & \textcolor{purple}{20,57} & \textcolor{purple}{12,67} & \textcolor{purple}{32,3}  & \textcolor{purple}{34,55} \\
        {6}                           & {2}    & {72,87}                             & {51,44}                             & {2,78}                                   & {60,82}                   & \textcolor{purple}{80,42} & {17,07}                   & \textcolor{purple}{13,45} & \textcolor{purple}{33,73} & \textcolor{purple}{33,64} \\
        {6}                           & {10}   & {73,61}                             & {48,73}                             & {2,82}                                   & \textcolor{purple}{32,64} & \textcolor{purple}{58,42} & \textcolor{purple}{33,12} & \textcolor{purple}{11,89} & \textcolor{purple}{33,15} & \textcolor{purple}{35,03} \\
        {6}                           & {16}   & {73,52}                             & {49,67}                             & {2,43}                                   & \textcolor{purple}{49,39} & \textcolor{purple}{73,19} & \textcolor{purple}{23,78} & \textcolor{purple}{13,06} & \textcolor{purple}{32,31} & \textcolor{purple}{34,64} \\
        {6}                           & {50}   & \textcolor{purple}{44,31}           & {45,07}                             & \textcolor{purple}{33,29}                & {\textbf{78,82}}          & {\textbf{90,22}}          & {\textbf{7,29}}           & \textcolor{purple}{12,72} & \textcolor{purple}{33,29} & \textcolor{purple}{32,99} \\
        {6}                           & {100}  & {\textbf{80,95}}                    & {\textbf{69,88}}                    & {\textbf{3,34}}                          & {62,2}                    & \textcolor{purple}{80,62} & \textcolor{purple}{19,88} & \textcolor{purple}{14,24} & \textcolor{purple}{32,36} & \textcolor{purple}{32,94} \\

@@

        $n$                           & $|V|$   & \textbf{A\textsubscript{shape}}     & \textbf{A\textsubscript{color}}     & \textbf{A\textsubscript{size}}           & \textbf{A\textsubscript{shape}} & \textbf{A\textsubscript{color}} & \textbf{A\textsubscript{size}} & \textbf{A\textsubscript{shape}} & \textbf{A\textsubscript{color}} & \textbf{A\textsubscript{size}} \\\midrule
        \multicolumn{2}{c|}{baseline} & {88,91} & {92,03}                             & {50,55}                             & {80,78}                                  & {89,38}                         & {49,92}                         & {100}                          & {90,78}                         & {76,72}                                                          \\\midrule
        {1}                           & {2}     & \textcolor{purple}{89,69}           & {93,68}                             & \textcolor{purple}{52,04}                & {88,09}                         & \textcolor{purple}{90,12}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{87,37}       & \textcolor{purple}{76,56}      \\
        {1}                           & {10}    & {96,31}                             & {94,21}                             & \textcolor{purple}{52,78}                & {90,6}                          & \textcolor{purple}{90,15}       & \textcolor{purple}{49,74}      & {100}                           & \textbf{91,32}                  & \textcolor{purple}{76,52}      \\
        {1}                           & {16}    & {94,97}                             & \textcolor{purple}{92,8}            & \textcolor{purple}{52,78}                & {91,97}                         & {93,45}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{91,03}       & \textcolor{purple}{76,52}      \\
        {1}                           & {50}    & \textcolor{purple}{90,1}            & \textcolor{purple}{91,58}           & \textcolor{purple}{52,78}                & {94,66}                         & {93,39}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,41}       & \textcolor{purple}{76,52}      \\
        {1}                           & {100}   & {90,41}                             & \textcolor{purple}{92,66}           & \textcolor{purple}{52,78}                & \textcolor{purple}{83,03}       & \textcolor{purple}{90,23}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,72}       & \textcolor{purple}{76,52}      \\
        {2}                           & {2}     & {92,45}                             & \textcolor{purple}{92,45}           & \textcolor{purple}{52,04}                & {88,72}                         & \textbf{94,38}                  & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,89}       & \textcolor{purple}{76,56}      \\
        {2}                           & {10}    & {96,09}                             & \textbf{94,44}                      & \textcolor{purple}{52,78}                & {91,54}                         & \textcolor{purple}{90,71}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,54}       & \textcolor{purple}{76,52}      \\
        {2}                           & {16}    & {90,58}                             & \textcolor{purple}{92,66}           & \textcolor{purple}{52,78}                & \textbf{97,18}                  & {94,14}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,98}       & \textcolor{purple}{76,52}      \\
        {2}                           & {50}    & {89,28}                             & \textcolor{purple}{92,45}           & \textcolor{purple}{52,78}                & {92,01}                         & {93,01}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,5}        & \textcolor{purple}{76,52}      \\
        {2}                           & {100}   & \textbf{98,91}                      & \textcolor{purple}{92,97}           & \textcolor{purple}{52,78}                & {92,66}                         & {92,49}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,68}       & \textcolor{purple}{76,52}      \\
        {3}                           & {2}     & {90,97}                             & {93,32}                             & \textcolor{purple}{52,04}                & {87,88}                         & {92,53}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{90,58}       & \textcolor{purple}{76,56}      \\
        {3}                           & {10}    & {97,01}                             & \textbf{{94,79}}                    & \textcolor{purple}{52,78}                & {94,4}                          & {92,8}                          & \textcolor{purple}{49,74}      & {100}                           & \textbf{91,17}                  & \textcolor{purple}{76,52}      \\
        {3}                           & {16}    & {95,36}                             & {93,1}                              & \textcolor{purple}{52,78}                & {86,72}                         & {91,88}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,06}       & \textcolor{purple}{76,52}      \\
        {3}                           & {50}    & {90,93}                             & \textcolor{purple}{90,84}           & \textcolor{purple}{52,78}                & {94,92}                         & \textbf{94,18}                  & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,59}       & \textcolor{purple}{76,52}      \\
        {3}                           & {100}   & \textcolor{purple}{89,37}           & \textcolor{purple}{90,76}           & \textcolor{purple}{52,78}                & {94,1}                          & {92,8}                          & \textcolor{purple}{49,74}      & {100}                           & \textbf{91,84}                  & \textcolor{purple}{76,52}      \\
        {4}                           & {2}     & {94,86}                             & \textcolor{purple}{92,11}           & \textcolor{purple}{52,04}                & {88,56}                         & {93,86}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{87,11}       & \textcolor{purple}{76,56}      \\
        {4}                           & {10}    & {90,58}                             & \textcolor{purple}{92,75}           & \textcolor{purple}{52,78}                & {95,05}                         & {93,71}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,89}       & \textcolor{purple}{76,52}      \\
        {4}                           & {16}    & \textbf{98,57}                      & {94,14}                             & \textcolor{purple}{52,78}                & \textbf{96,14}                  & \textbf{95,23}                  & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,06}       & \textcolor{purple}{76,52}      \\
        {4}                           & {50}    & {95,66}                             & {93,32}                             & \textcolor{purple}{52,78}                & {91,01}                         & \textcolor{purple}{90,45}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,85}       & \textcolor{purple}{76,52}      \\
        {4}                           & {100}   & \textcolor{purple}{89,41}           & {93,58}                             & \textcolor{purple}{52,78}                & {94,66}                         & {93,19}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,98}       & \textcolor{purple}{76,52}      \\
        {6}                           & {2}     & {93,39}                             & {92,94}                             & \textcolor{purple}{52,04}                & \textcolor{purple}{82,18}       & {92,16}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{90,05}       & \textcolor{purple}{76,56}      \\
        {6}                           & {10}    & \textbf{98,78}                      & \textbf{94,23}                      & \textcolor{purple}{52,78}                & \textbf{96,79}                  & {92,75}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{87,67}       & \textcolor{purple}{76,52}      \\
        {6}                           & {16}    & {96,96}                             & \textcolor{purple}{91,32}           & \textcolor{purple}{52,78}                & {95,57}                         & {93,75}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,37}       & \textcolor{purple}{76,52}      \\
        {6}                           & {50}    & \textcolor{purple}{88,28}           & \textcolor{purple}{91,45}           & \textcolor{purple}{52,78}                & {91,71}                         & \textcolor{purple}{86,24}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,32}       & \textcolor{purple}{76,52}      \\
        {6}                           & {100}   & {94,92}                             & \textcolor{purple}{92,45}           & \textcolor{purple}{52,78}                & {95,3}                          & {93,62}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,19}       & \textcolor{purple}{76,52}      \\

@@

Finally, Table \ref{tab:results:attribute-predictor-game} shows the results for the games in which the receiver predicts a one-hot vector of the attributes.
Again, the baselines are games, the receiver plays alone.
Hereby, it can be seen that the receiver can already predict the \emph{shape} and \emph{color}  very well: 88,91\% and 92\% respectively on the \emph{Dale-2} dataset, 80,78\% and 89,38\% respectively on the \emph{Dale-5} dataset, and 100\% and 90,78\% respectively on the \emph{CLEVR color} dataset.
The \emph{size} however corresponds to a random guess on the \emph{Dale} dataset and only achieves 76,72\% on the \emph{CLEVR color} dataset.
This shows that the receiver can already identify attributes of the target object on their own and discriminate it from the distractors.
However, the size still seems to be an attribute which is difficult to extract from the visual scene.
The increase in performance compared to the generation of referring expression can be explained by two reasons:
First, the complexity of the receiver is greatly reduced.
When only predicting one-hot vectors, much fewer layers and weights are involved that need to be trained and hence the models can learn the given task.
Secondly, the complexity of the task is reduced as well.
The generation of referring expressions not only includes the learning of the tokens (and their embeddings), but also their order in the referring expression and their salience for the incremental algorithm.
Using one-hot vectors, both order and salience are irrelevant and only the attributes themselves are needed to be learned.
The goal of these experiments is now to see if the information of the sender improves the predictions of the receiver.

As can be seen in the table, the improvement is dependent on the attributes.
When the agents are trained on the \emph{Dale-2} dataset, almost all configurations improve the prediction of the shape.
While 11 out of 30 configurations only improve by a maximum of 2\% points, most can predict the \emph{shape} much better, with an accuracy of up to 98,91\%.
A pattern based on the vocabulary size $|V|$ and message length $n$ is however difficult to identify.
A smaller vocabulary size of $|V|=10$ generally fares well, but also a large vocabulary size of $|V|=100$ can help to predict the shape both with short messages ($n=2$) and long messages ($n=6$).
Opposed to the \emph{shape}, the prediction of the \emph{color} can only be improved by a small margin of a maximum of 2,7\% points.
Most of the configurations produce the same or slightly worse results than the baseline.
Again, a vocabulary of $|V|=10$ seems to help the most.
Interestingly, when the agents can only use one token to encode their message ($|V|=2$), an improvement of predictions of the \emph{shape} comes to the expense of the accuracy of the \emph{color} and vice versa.
This indicates that the sender doesn't have enough space to communicate both attributes to the receiver.
Looking at the \emph{size}, a constant improvement of 2\% points across all configurations can be seen.
The final accuracy however still lies slightly above a random guess.

The results are similar when the agents need to describe the \emph{Dale-5} dataset.
The baseline accuracies of the \emph{shape} and \emph{color} are lower, but can be improved to similar peaks as for the \emph{Dale-2} dataset.
The highest accuracy for the \emph{shape} lies at 97,18\%, while it lies at 95,23\% for the \emph{color}.
This indicates that the larger number of distractors makes it difficult to focus on the correct object and instead describes distractors when the receiver is on their own.
But when the sender can communicate the correct object, the receiver describes the attributes as well as with fewer distractors.
As before, the predictions of the \emph{size} correspond to a random guess.

Using the \emph{CLEVR color} dataset, almost no improvements can be seen.
The predictions of the \emph{shape} stay at 100\% accuracy, while the predictions of the \emph{color} get slightly worse for most configurations and if they improve they only improve by maximum 1\% point.
The predictions of the \emph{size} stay the same.
The fact that the sender has a smaller influence on the \emph{CLEVR color} dataset than on the \emph{Dale} dataset is surprising since the sender would need to communicate only the \emph{color} instead of additionally the \emph{shape} (and \emph{size}).
A reason why this happens might be the larger number of distractors.
This number might hinder the receiver to converge and understand the task, by connecting the one-hot vector to the colors of the target object.
While for the \emph{Dale} datasets the receiver has a choice between only 2 to 5 objects, they need to decide between up to 10 objects on the \emph{CLEVR color} dataset.
That might confuse the model where to focus on and subsequently to connect it to the on-hot vector.
Future experiments with a similar dataset including fewer distractors would need to verify this hypothesis.

Concluding, these experiments show that the models are able to extract and communicate information about the \emph{shape} and \emph{color} from the images when few objects are present.
When the agents are forced to generate referring expressions which are more complex in their structure, they produce perfect results less frequently.
However, the communication is successfully very often as it helps the receiver in identifying the correct attributes and referring expression.
